Continuous voting by approval and participation

### 2015-05-11 ApresentacoesArtigos/collectiveRanking/paper.tex
qualis pub votacao
terminada descricao da correcao de alpha_i

\begin{equation}
\begin{split}
\eta_i > \overline{\eta}    \;\;\;\;\;\; & \Rightarrow\;\;\;\;\;\; i     \text{ is sampled} \\
\gamma_i>\overline{\gamma}    \;\;\;\;\;\; & \Rightarrow\;\;\;\;\;\; i    \text{ is relevant} \\
|\alpha_i| \leq\overline{\alpha}\;\;\;\;\;\; & \Rightarrow\;\;\;\;\;\; i  \text{ is a clash} \\
\alpha_i > \overline{\alpha}  \;\;\;\;\;\; & \Rightarrow\;\;\;\;\;\; i    \text{ is approved} \\
-\alpha_i > \overline{\alpha} \;\;\;\;\;\; & \Rightarrow\;\;\;\;\;\; i   \text{ is disapproved} \\
\end{split}
\end{equation}

If a proposal is both sampled and relevant, than it is prioritized.
The coherent values of $\overline{\alpha_i}=0.5$ (or $1/3$)
and $\overline{\gamma_i}=0.5$ were chosen as standards of the decision model. 
These are likely to change with implementation and management.

@@

\begin{equation*}
\begin{split}
\overline{\gamma_i} & =1-\frac{\eta_i}{max(\{\eta_j , \;\forall\; j \})} \\
\overline{\alpha_i} & = 1-\gamma_i
\end{split}
\end{equation*}
\noindent These bonds among proposal variables has been discarded by the staff in the present initial steps.

% notive that threasholds can be taken as different for each proposal: \overline{\alpha_i}=1-\eta_i/\eta_{max}

\vfill
\vspace{.6cm}
\vfill

>>>>

\begin{equation}
\begin{split}
\eta_i > \overline{\eta}    \;\;\;\;\;\; & \Rightarrow    \;\;\;\;\;\; i     \text{ is sampled} \\
\gamma_i>\overline{\gamma}    \;\;\;\;\;\; & \Rightarrow  \;\;\;\;\;\; i    \text{ is relevant} \\
|\alpha_i| \leq\overline{\alpha}\;\;\;\;\;\; & \Rightarrow\;\;\;\;\;\; i  \text{ is a clash} \\
\alpha_i > \overline{\alpha}  \;\;\;\;\;\; & \Rightarrow  \;\;\;\;\;\; i    \text{ is approved} \\
-\alpha_i > \overline{\alpha} \;\;\;\;\;\; & \Rightarrow  \;\;\;\;\;\; i   \text{ is disapproved} \\
\end{split}
\end{equation}

If a proposal is both sampled and relevant, than it is prioritized.
The values of $\overline{\alpha_i}=0.5$ (or $1/3$)
and $\overline{\gamma_i}=0.5$ were chosen as standards of the decision model. 
These are likely to change with implementation and management.

@@

\begin{equation*}
\begin{split}
\overline{\gamma_i} & =1-\frac{\eta_i}{max(\{\eta_j , \;\forall\; j \})} \\
\overline{\alpha_i} & = 1-\gamma_i
\end{split}
\end{equation*}
\noindent These bonds among proposal variables has been discarded by the staff in the present initial steps.
\pagebreak

\subsection{Ranking proposals in the user interface}
This voting setting presents a challenge to the user interface.
Above all, the space within the ranking page allocated to each proposal gathers all of them, both the newest and the oldest.

Solutions were given to this problems in some of the frameworks presented in the next section.
Random ranking is the only of them that can be applied to our setting. A novel approach is in use by
the development team, with $\hat{\eta_i}$ defined as:

\begin{equation}
\begin{split}
\frac{\eta_{max}-\eta_{min}}{2}\leq\eta_i    \;\;\;\;\;\;\Rightarrow \;\;\;\;\;\;\hat{\eta}=\eta_i-\eta_{min} \\
\frac{\eta_{max}-\eta_{min}}{2}>\eta_i \;\;\;\;\;\;\Rightarrow \;\;\;\;\;\;\hat{\eta}=\eta_{max}-\eta_i
\end{split}                                           
\end{equation}

\noindent allowing the calculation of $\hat{\alpha_i}$ as:

\begin{equation}
	\begin{split}\label{eq:a1}
	\hat{\alpha_i}=\frac{v^+_i-v^-_i}{\hat{\eta_i}} \\
\end{split}                                           
\end{equation}                                       
or
\begin{equation}
	\begin{split}\label{eq:a2}
	\hat{\alpha_i}=\frac{\alpha_i}{\hat{\eta_i}} \\
\end{split}                                           
\end{equation}

Compared to $\alpha_i$, the $\hat{\alpha_i}$ has the drawback of the complexity but the
desired advantage of giving higher values for proposals with $\eta_i$ near the average.
Both newest and oldest proposals are regarded as less important, having the fewest sampling (newest proposals)
or being already considered by public managers (oldest proposals). A major problem is that it can be argued that
Equation~\ref{eq:a1} is little or no informative, as it is calculated by the relation of the
absolute difference $v^+_i-v^-_i$ and $\hat{\eta_i}$, which is not proportional to $\eta_i$. Therefore, Equation~\ref{eq:a2} is currently preferred by the development team.

%\vfill
%\vspace{.6cm}
%\vfill
